A Graph Theoretic Approach to Problem Formulation for Multidisciplinary Design Analysis and Optimization

### 2013-05-10 conclusions.tex
last tweaks

For simple problems with few analysis tools and variables, the formulation of a 
valid problem description is straightforward.  However, MDAO problems continue to 
grow in scale and complexity. As the numbers of analysis tools and variables have 
increased, it has become increasingly challenging and time consuming for engineering 
teams to determine how the multiple analysis tools can be interconnected to produce 
valid problem formulations. Large complex problems also present signficant challenges
as the design process evolves requiring the integration of additional and higher-fidelity 
analysis tools into an existing model. The graph syntax presented in this paper 
is intended to offer value in this context of increasing problem complexity by 
providing a formal approach to identify and resolve data conflicts in a set of interconnected
analysis tools and to help arrange those tools into an effective and efficient system model
where MDAO tools and techniques can be quickly and easily applied.

>>>>

For simple problems with few analysis tools and variables, the formulation of a 
valid problem description is straightforward.  However, MDAO problems continue to 
grow in scale and complexity. As the numbers of analysis tools and variables have 
increased, it has become increasingly challenging and time consuming for engineering 
teams to determine how the multiple analysis tools can be interconnected to produce 
valid problem formulations. Large complex problems also present signficant challenges
as the design process evolves requiring the integration high-fidelity 
analysis tools into an existing model. The graph syntax presented in this paper 
is intended to offer value in this context of increasing problem complexity by 
providing a formal approach to identify and resolve data conflicts in a set of interconnected
analysis tools and to help arrange those tools into an effective and efficient system model
where MDAO tools and techniques can be quickly and easily applied.
